Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-27 TACAS2018/paper.tex

The CEGIS-OR loop for this approach is described next.
We make use of two abstractions corresponding to two
specifications: $\phi_{synth}$ used by the synthesiser and
$\phi_{static}$ which is given to the synthesis refinement loop. 
Both specifications will be updated during execution and new abstractions will be constructed for each.
Let us define the properties 
\begin{align*}
\phi_{\langle C \rangle}&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
\phi_{dynamics}^{T_d}&:= \mat{A}_d, \mat{B}_d, \mat{C}_d
\end{align*}
The first one defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$) and its effect on the system dynamics.
The second one defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
We start our loop with 
\begin{align*}
\phi_{synth}&:=\phi_{dynamics}^{T_d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
\phi_{static}&:=\phi_{synth} \wedge \phi_{\langle C \rangle}.
\end{align*}
These specifications will vary as the loop progresses.  We only note that at all times $\phi_{static} \models \phi_{synth}$.
Let us see how the loop updates these specifications.

>>>>

The CEGIS-OR loop for this approach is described next.
We make use of two abstractions corresponding to two
specifications: $\phi_{synth}$ used by the synthesiser and
$\phi_{static}$ which is given to the optimiser. 
Both specifications are updated during execution and new abstractions are constructed for each.
Let us define the properties 
\begin{align*}
\phi_{\langle C \rangle}&:= \mat{K}=\mat{K}_{\langle C \rangle} \wedge \mat{L}=\mat{L}_{\langle C \rangle}\\
\phi_{dynamics}^{T_d}&:= \{\mat{A}_d, \mat{B}_d, \mat{C}_d \mid \mat{A}_d=e^{\mat{A}T_d}\}
\end{align*}
$\phi_{\langle C \rangle}$ defines the word length of the digital controller ($\mathbb{R}_{\langle C \rangle}$)
and $\phi_{dynamics}^{T_d}$ defines the sampling time ($T_d$) and its effect on the system dynamics (as per Section \ref{sec:continuous_time_accel}).
We start our loop with 
\begin{align*}
\phi_{synth}&:=\phi_{dynamics}^{T_d} \wedge \phi_{stability} \wedge \phi_{input} \wedge \phi_{init}\\
\phi_{static}&:=\phi_{synth} \wedge \phi_{\langle C \rangle}.
\end{align*}
These specifications will vary as the loop progresses.  However, at all times $\phi_{static} \models \phi_{synth}$.
Let us see how the loop updates these specifications.
